Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-28 Markdown Documents/Manuscript.Rmd
added difference columns and a barbell plot to lost revenue

```{r echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE, fig.height = 6, fig.width = 12}
dat%>%filter(UnitCode %in% fitsig$Par)%>%group_by(ParkName)%>%
  summarise(totrec=sum(RecreationVisits),totpred=sum(PredNoSmoke50CI))%>%ungroup()%>%
  mutate(diff=totpred-totrec)%>%
ggplot(., 
       aes(y = reorder(ParkName,diff),
           x = totrec,
           xend = totpred)) +  
  ggalt::geom_dumbbell(size = 1.2,
                       size_x = 5, 
                       size_xend = 5,
                       colour = "darkgrey", 
                       colour_x = "black", 
                       colour_xend = "#1f78b4",dot_guide = T,dot_guide_size = NULL,dot_guide_colour = "lightgrey") +
   annotate("text", x = 60000000, y = "Yosemite NP", label = "Observed visitation",vjust=-1,hjust=1,fontface=2)+
  annotate("text", x = 75000000, y = "Yosemite NP", label = "Predicted visitation no smoke",vjust=-1,color="#1f78b4",fontface=2)+
  scale_x_continuous( breaks=seq(10000000,90000000,20000000),labels = scales::comma) + 
  labs(title = "Total Lost Visitation",
       subtitle = "1980 to 2018",
       x = "Total Visits",
       y = "")+theme_classic()+mytheme+theme(plot.subtitle = element_text(face = "bold"))

@@

We can apply these visitation estimates to the fee data/predictions also. This gives us the following table.
```{r echo=FALSE, cache=TRUE}

formattable::formattable(summaryFinancialLoss)
```

>>>>

```{r echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE, fig.height = 8, fig.width = 13}
dat%>%filter(UnitCode %in% fitsig$Par)%>%group_by(ParkName)%>%
  summarise(totrec=sum(RecreationVisits),totpred=sum(PredNoSmoke50CI))%>%ungroup()%>%
  mutate(diff=totpred-totrec)%>%
  ggplot(., 
         aes(y = reorder(ParkName,diff),
             x = totrec,
             xend = totpred)) +  
  ggalt::geom_dumbbell(size = 1.2,
                       size_x = 5, 
                       size_xend = 5,
                       colour = "darkgrey", 
                       colour_x = "black", 
                       colour_xend = "#1f78b4",dot_guide = T,dot_guide_size = NULL,dot_guide_colour = "lightgrey") +
  geom_rect( aes(xmin=91000000, xmax=99000000, ymin=-Inf, ymax=Inf), fill="grey") +
  geom_text( aes(label=paste0("-",round((diff/totrec)*100,digits=1), "%"), y=ParkName, x=95000000), fontface=2, size=4)+
  annotate("text", x = 95000000, y = "Glacier NP", label = "Difference",vjust=-1.5,fontface=2)+
  annotate("text", x = 60000000, y = "Yosemite NP", label = "Observed visitation",vjust=-1,hjust=1,fontface=2)+
  annotate("text", x = 75000000, y = "Yosemite NP", label = "Predicted visitation no smoke",vjust=-1,color="#1f78b4",fontface=2)+
  scale_x_continuous( breaks=seq(10000000,90000000,20000000),labels = scales::comma) + 
  labs(title = "Total Lost Visitation",
       subtitle = "1980 to 2018",
       x = "Total Visits",
       y = "")+theme_classic()+mytheme+theme(plot.subtitle = element_text(face = "bold"))

@@

We can apply these visitation estimates to the fee data/predictions also.
```{r echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE, fig.height = 8, fig.width = 13}
financialData<-merge(dat[,c(2,5)],financialData,by="UnitCode")
financialData%>%filter(UnitCode %in% fitsig$Par)%>%group_by(ParkName)%>%
  summarise(sumincome=sum(incomeObserved),sumincomePred=sum(incomePred))%>%ungroup()%>%
  mutate(diff=sumincomePred-sumincome)%>%
  ggplot(., 
         aes(y = reorder(ParkName,diff),
             x = sumincome,
             xend = sumincomePred)) +  
  ggalt::geom_dumbbell(size = 1.2,
                       size_x = 5, 
                       size_xend = 5,
                       colour = "darkgrey", 
                       colour_x = "black", 
                       colour_xend = "#b2df8a",dot_guide = T,dot_guide_size = NULL,dot_guide_colour = "lightgrey")+
  geom_rect( aes(xmin=100500000000, xmax=109500000000, ymin=-Inf, ymax=Inf), fill="grey") +
  geom_text( aes(label=paste0("-",round((diff/sumincome)*100,digits=1), "%"), y=ParkName, x=105000000000), fontface=2, size=4)+
  annotate("text", x = 105000000000, y = "Glacier NP", label = "Difference",vjust=-1.5,fontface=2)+
  scale_x_continuous( labels = scales::dollar_format(prefix = "$")) +
  annotate("text", x = 62000000000, y = "Yosemite NP", label = "Observed fee revenue",vjust=-1,hjust=1,fontface=2)+
  annotate("text", x = 80000000000, y = "Yosemite NP", label = "Predicted fee revenue no smoke",vjust=-1,color="#b2df8a",fontface=2)+
  labs(title = "Total Lost Revenue",
       subtitle = "1980 to 2018",
       x = "Total Visitor Revenue 1980 to 2018",
       y = "")+theme_classic()+mytheme+theme(plot.subtitle = element_text(face = "bold"))
